TODO

### 2021-05-06 paper2/sec-schemechange.tex
Add placeholder for initial-state photons

At LO in $\alpha$, the coupling $\alpha$ in the PDF (as used in the evolution equations) and in the fixed-order calculations can be chosen independently.
This is important, because in the PDFs the coupling is typically assumed to be renormalised in the $\overline{\mathrm{MS}}$ scheme, while in fixed-order calculations $\alpha$ is usually chosen according to the $G_\mu$ scheme.

>>>>

At LO in $\alpha$, the coupling $\alpha$ in the PDF (as used in the evolution equations) and in the fixed-order calculations can be chosen independently, if no initial-state photons are present.
\textbf{TODO}: Marco insert discussion here, and change the next sentence accordingly.

This is important, because in the PDFs the coupling is typically assumed to be renormalised in the $\overline{\mathrm{MS}}$ scheme, while in fixed-order calculations $\alpha$ is usually chosen according to the $G_\mu$ scheme.
